---
title: "Results for MSE defined by correlation"
author: "Yuying Tan"
date: "4/4/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

```{r, include=FALSE}
load('bvmddata.RData')
library(maditr)
library(Johnson)
library(rstatix)
library(ggpubr)
library(tidyverse)
```

The true synchrony is defined as the values of correlation.

# General results
```{r}
bvmddata[,3]<-factor(bvmddata[,3],levels=c('rlow','ravg',"rhigh"))
bvmddata$timelength <- factor(bvmddata$timelength,levels=c('1006','10054'))
bvmddata$synchr_method <- factor(bvmddata$synchr_method,levels=c('coherence','phasesynchrony','Kullback','Renyi01','Renyi05','Renyi09','JensenShannon','JensenRenyi2','JensenRenyi6','JensenRenyi10','mutual_information'))
bvmddata$synchr_method <- factor(bvmddata$synchr_method,levels=c('coherence','phasesynchrony','Kullback','Renyi01','Renyi05','Renyi09','JensenShannon','JensenRenyi2','JensenRenyi6','JensenRenyi10','mutual_information'),labels=c('coherence','phase synchrony','KL','R(01)','R(05)','R(09)','JS','JR(2)','JR(6)','JR(10)','MI'))
```

```{r}
bvmddata %>%
  group_by(synchr_method) %>%
  summarise(mean_MSE=mean(MSE_c)) %>%
  arrange(mean_MSE)
```
# Overall influnece of data characteristics


```{r}
maineffects_truesynchrony <- bvmddata %>%
  group_by(synchr_method,true_synchrony)  %>%
  summarise(mean_MSE=mean(MSE_c))

maineffects_kappa <- bvmddata %>%
  group_by(synchr_method,kappa)  %>%
  summarise(mean_MSE=mean(MSE_c))

maineffects_tlag <- bvmddata %>%
  group_by(synchr_method,tlag)  %>%
  summarise(mean_MSE=mean(MSE_c))

maineffects_timelength <- bvmddata %>%
  group_by(synchr_method,timelength)  %>%
  summarise(mean_MSE=mean(MSE_c))

maineffects_noiselevel <- bvmddata %>%
  group_by(synchr_method,noiselevel)  %>%
  summarise(mean_MSE=mean(MSE_c))

maineffects_noisetype <- bvmddata %>%
  group_by(synchr_method,noisetype)  %>%
  summarise(mean_MSE=mean(MSE_c))
colnames(maineffects_kappa)[2] <- 'level'
colnames(maineffects_truesynchrony)[2] <- 'level'
colnames(maineffects_timelength)[2] <- 'level'
colnames(maineffects_noiselevel)[2] <- 'level'
colnames(maineffects_noisetype)[2] <- 'level'
colnames(maineffects_tlag)[2] <- 'level'

maineffects <- rbind(maineffects_truesynchrony,maineffects_kappa,maineffects_tlag,maineffects_timelength,maineffects_noiselevel,maineffects_noisetype)
a <- rbind(dcast(maineffects_kappa, level ~  synchr_method),
dcast(maineffects_truesynchrony, level ~  synchr_method),
dcast(maineffects_timelength, level ~  synchr_method),
dcast(maineffects_noiselevel, level ~  synchr_method),
dcast(maineffects_noisetype, level ~  synchr_method),
dcast(maineffects_tlag, level ~  synchr_method))
factor <- c('kappa','kappa','kappa','true_synchrony','true_synchrony','true_synchrony','timelength','timelength','noiselevel','noiselevel','noisetype','noisetype','tlag','tlag')
a <- cbind(factor,a)
a
rowMeans(a[,3:12])
rowMeans(a[,3:13])
options(digits = 3)
```


# Mixed ANOVA
Significant effects with generalized effect size greater than 0.5 are discussed.

```{r}
Sevenway <- anova_test(
  data = bvmddata, dv = MSE_c, wid = id,
  between = c(true_synchrony,kappa,tlag,timelength,noiselevel,noisetype), within = synchr_method)
effects_table <- cbind(get_anova_table(Sevenway)$Effect,get_anova_table(Sevenway)$DFn,get_anova_table(Sevenway)[,4],get_anova_table(Sevenway)$p,get_anova_table(Sevenway)$ges)
pvalue <- as.numeric(effects_table[,4])
ges <- as.numeric(effects_table[,5])
DF <- as.numeric(effects_table[,2])
Fvalue <- as.numeric(effects_table[,3]) 
effects_table <- data.frame(effects_table[,1],DF,Fvalue,pvalue,ges)
colnames(effects_table)[1] <- 'effects'
effects <- effects_table%>%
  arrange(desc(ges))
effects[1:18,]
```

### Interaction between 'synchr_method' and 'timelength'
Including mutual information:



Excluding mutual information:


```{r}
bvmddata2 <- bvmddata[bvmddata$synchr_method!='MI',]
data2 <- bvmddata2 %>% 
  group_by(synchr_method,timelength) %>% 
  summarise(y_mean = mean(MSE_c))
data2 %>% 
  ggplot() +
   aes(x = timelength, y = y_mean, group = synchr_method) +
   geom_line(aes(color = synchr_method,linetype=synchr_method))+
  ylab('Mean of MSEs')+scale_color_manual(values=c('black','green','hotpink','red','red','red','blue','purple','purple','purple','orange'),name='Synchrony method')+scale_linetype_manual(values = c("solid", "solid","solid","solid","dashed","dotted","solid","solid","dashed","dotted",'solid'),name='Synchrony method')+xlab('Time length')
```


### Interaction between 'true_synchrony', 'kappa' and 'synchr_method'

Excluding mutual information:

'kappa' is equal to 0.5:


```{r}
bvmddata3 <- bvmddata[bvmddata$kappa=='0.5',]

bvmddata4 <- bvmddata3[bvmddata3$synchr_method!='MI',]
data2 <- bvmddata4 %>% 
  group_by(synchr_method,true_synchrony) %>% 
  summarise(y_mean = mean(MSE_c))
data2 %>% 
   ggplot() +
   aes(x = true_synchrony, y = y_mean, group = synchr_method) +
   geom_line(aes(color = synchr_method,linetype=synchr_method))+
  ylab('Mean of MSEs')+scale_color_manual(values=c('black','green','hotpink','red','red','red','blue','purple','purple','purple','orange'),name='Synchrony method')+scale_linetype_manual(values = c("solid", "solid","solid","solid","dashed","dotted","solid","solid","dashed","dotted",'solid'),name='Synchrony method')+xlab('True synchrony')+scale_x_discrete('True synchrony',labels=c('low','avg','high'),limits=c('rlow','ravg','rhigh'))+ylim(0,0.5)
```

'kappa' is equal to 1:

```{r}
bvmddata5 <- bvmddata[bvmddata$kappa=='1',]

bvmddata6 <- bvmddata5[bvmddata5$synchr_method!='MI',]
data2 <- bvmddata6 %>% 
  group_by(synchr_method,true_synchrony) %>% 
  summarise(y_mean = mean(MSE_c))
data2 %>% 
   ggplot() +
   aes(x = true_synchrony, y = y_mean, group = synchr_method) +
   geom_line(aes(color = synchr_method,linetype=synchr_method))+
  ylab('Mean of MSEs')+scale_color_manual(values=c('black','green','hotpink','red','red','red','blue','purple','purple','purple','orange'),name='Synchrony method')+scale_linetype_manual(values = c("solid", "solid","solid","solid","dashed","dotted","solid","solid","dashed","dotted",'solid'),name='Synchrony method')+xlab('Time length')+xlab('True synchrony')+scale_x_discrete('True synchrony',labels=c('low','avg','high'),limits=c('rlow','ravg','rhigh'))+ylim(0,0.5)
```

'kappa' is equal to 2:


```{r}
bvmddata7 <- bvmddata[bvmddata$kappa=='2',]

bvmddata8 <- bvmddata7[bvmddata7$synchr_method!='MI',]
data2 <- bvmddata8 %>% 
  group_by(synchr_method,true_synchrony) %>% 
  summarise(y_mean = mean(MSE_c))
data2 %>% 
  ggplot() +
   aes(x = true_synchrony, y = y_mean, group = synchr_method) +
   geom_line(aes(color = synchr_method,linetype=synchr_method))+
  ylab('Mean of MSEs')+scale_color_manual(values=c('black','green','hotpink','red','red','red','blue','purple','purple','purple','orange'),name='Synchrony method')+scale_linetype_manual(values = c("solid", "solid","solid","solid","dashed","dotted","solid","solid","dashed","dotted",'solid'),name='Synchrony method')+xlab('Time length')+xlab('True synchrony')+scale_x_discrete('True synchrony',labels=c('low','avg','high'),limits=c('rlow','ravg','rhigh'))+ylim(0,0.5)
```



