---
title: "Results for correlation defined by r"
author: "Yuying Tan"
date: "4/4/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

```{r, include=FALSE}
load('bvmddata.RData')
library(maditr)
library(Johnson)
library(rstatix)
library(ggpubr)
library(tidyverse)
```

The true synchrony is defined as the values of r.

# General results
Coherence and phase synchrony perform much better than other synchrony methods, but the mean correlations are smaller than 0.2, so overall the two methods also do not perform well.

```{r}
bvmddata %>%
  group_by(synchr_method) %>%
  summarise(mean_correlation=mean(correlation)) %>%
  arrange(desc(mean_correlation))
```
# Overall influnece of data characteristics

```{r}
bvmddata[,3]<-factor(bvmddata[,3],levels=c('rlow','ravg',"rhigh"))
bvmddata$timelength <- factor(bvmddata$timelength,levels=c('1006','10054'))
bvmddata$synchr_method <- factor(bvmddata$synchr_method,levels=c('coherence','phasesynchrony','Kullback','Renyi01','Renyi05','Renyi09','JensenShannon','JensenRenyi2','JensenRenyi6','JensenRenyi10','mutual_information'))
bvmddata$synchr_method <- factor(bvmddata$synchr_method,levels=c('coherence','phasesynchrony','Kullback','Renyi01','Renyi05','Renyi09','JensenShannon','JensenRenyi2','JensenRenyi6','JensenRenyi10','mutual_information'),labels=c('coherence','phase synchrony','KL','R(01)','R(05)','R(09)','JS','JR(2)','JR(6)','JR(10)','MI'))

```



```{r}
maineffects_truesynchrony <- bvmddata %>%
  group_by(synchr_method,true_synchrony)  %>%
  summarise(mean_correlation=mean(correlation))

maineffects_kappa <- bvmddata %>%
  group_by(synchr_method,kappa)  %>%
  summarise(mean_correlation=mean(correlation))

maineffects_tlag <- bvmddata %>%
  group_by(synchr_method,tlag)  %>%
  summarise(mean_correlation=mean(correlation))

maineffects_timelength <- bvmddata %>%
  group_by(synchr_method,timelength)  %>%
  summarise(mean_correlation=mean(correlation))

maineffects_noiselevel <- bvmddata %>%
  group_by(synchr_method,noiselevel)  %>%
  summarise(mean_correlation=mean(correlation))

maineffects_noisetype <- bvmddata %>%
  group_by(synchr_method,noisetype)  %>%
  summarise(mean_correlation=mean(correlation))
colnames(maineffects_kappa)[2] <- 'level'
colnames(maineffects_truesynchrony)[2] <- 'level'
colnames(maineffects_timelength)[2] <- 'level'
colnames(maineffects_noiselevel)[2] <- 'level'
colnames(maineffects_noisetype)[2] <- 'level'
colnames(maineffects_tlag)[2] <- 'level'

maineffects <- rbind(maineffects_truesynchrony,maineffects_kappa,maineffects_tlag,maineffects_timelength,maineffects_noiselevel,maineffects_noisetype)
a <- rbind(dcast(maineffects_kappa, level ~  synchr_method),
dcast(maineffects_truesynchrony, level ~  synchr_method),
dcast(maineffects_timelength, level ~  synchr_method),
dcast(maineffects_noiselevel, level ~  synchr_method),
dcast(maineffects_noisetype, level ~  synchr_method),
dcast(maineffects_tlag, level ~  synchr_method))
factor <- c('kappa','kappa','kappa','true_synchrony','true_synchrony','true_synchrony','timelength','timelength','noiselevel','noiselevel','noisetype','noisetype','tlag','tlag')
a <- cbind(factor,a)
a2 <- rowMeans(a[,3:13])
options(digits = 2)
charac <- cbind(a,a2)
print(xtable(charac, type = "latex"), file = "characteristics_corbr.tex",include.rownames = F)

```


# Mixed ANOVA
```{r}
hist(bvmddata$correlation,main='Correlation')
```
```{r}
library(Johnson)
library(rstatix)
library(ggpubr)
```


Normality for correlation and transformed correlation:

```{r,echo=F}
ggqqplot(bvmddata, "correlation", ggtheme = theme_bw()) +
  facet_grid(kappa ~ synchr_method, labeller = "label_both")

```

```{r}
bvmddata %>%
  group_by(synchr_method) %>%
  levene_test(correlation~kappa*true_synchrony*noisetype*tlag*timelength*noiselevel)

```

Significant effects with generalized effect size greater than 0.1 are discussed.

```{r}
Sevenway <- anova_test(
  data = bvmddata, dv = correlation, wid = id,
  between = c(true_synchrony,kappa,tlag,timelength,noiselevel,noisetype), within = synchr_method)
effects_table <- cbind(get_anova_table(Sevenway)$Effect,get_anova_table(Sevenway)$DFn,get_anova_table(Sevenway)[,4],get_anova_table(Sevenway)$p,get_anova_table(Sevenway)$ges)
pvalue <- as.numeric(effects_table[,4])
ges <- as.numeric(effects_table[,5])
DF <- as.numeric(effects_table[,2])
Fvalue <- as.numeric(effects_table[,3]) 
effects_table <- data.frame(effects_table[,1],DF,Fvalue,pvalue,ges)
colnames(effects_table)[1] <- 'effects'
effects <- effects_table%>%
  arrange(desc(ges))
effects[1:18,]
``` 


