---
title: "Results (MSE) for henon maps with true synchrony defined by correlation"
author: "Yuying Tan"
date: "3/30/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(maditr)
load('datahenon.RData')
library(Johnson)
library(rstatix)
library(ggpubr)
library(tidyverse)
```
The true synchrony is defined as the values of the results of correlation coefficient.

# General results
```{r}
datahenon[,2]<-factor(datahenon[,2],levels=c('rlow','ravg',"rhigh"))
datahenon$timelength <- factor(datahenon$timelength,levels=c('1006','10054'))
datahenon$synchr_method <- factor(datahenon$synchr_method,levels=c('coherence','phasesynchrony','Kullback','Renyi01','Renyi05','Renyi09','JensenShannon','JensenRenyi2','JensenRenyi6','JensenRenyi10','mutual_information'))
datahenon$synchr_method <- factor(datahenon$synchr_method,levels=c('coherence','phasesynchrony','Kullback','Renyi01','Renyi05','Renyi09','JensenShannon','JensenRenyi2','JensenRenyi6','JensenRenyi10','mutual_information'),labels=c('coherence','phase synchrony','KL','R(01)','R(05)','R(09)','JS','JR(2)','JR(6)','JR(10)','MI'))
datahenon2 <- datahenon[datahenon$synchr_method!='MI',]
```

```{r}
datahenon %>%
  group_by(synchr_method) %>%
  summarise(mean_MSE=mean(MSE_c)) %>%
  arrange(mean_MSE)

```
# Overall influnece of data characteristics


```{r}
maineffects_truesynchrony <- datahenon %>%
  group_by(synchr_method,true_synchrony)  %>%
  summarise(mean_MSE=mean(MSE_c))

maineffects_bd <- datahenon %>%
  group_by(synchr_method,bd)  %>%
  summarise(mean_MSE=mean(MSE_c))

maineffects_tlag <- datahenon %>%
  group_by(synchr_method,tlag)  %>%
  summarise(mean_MSE=mean(MSE_c))

maineffects_timelength <- datahenon %>%
  group_by(synchr_method,timelength)  %>%
  summarise(mean_MSE=mean(MSE_c))

maineffects_noiselevel <- datahenon %>%
  group_by(synchr_method,noiselevel)  %>%
  summarise(mean_MSE=mean(MSE_c))

maineffects_noisetype <- datahenon %>%
  group_by(synchr_method,noisetype)  %>%
  summarise(mean_MSE=mean(MSE_c))
colnames(maineffects_bd)[2] <- 'level'
colnames(maineffects_truesynchrony)[2] <- 'level'
colnames(maineffects_timelength)[2] <- 'level'
colnames(maineffects_noiselevel)[2] <- 'level'
colnames(maineffects_noisetype)[2] <- 'level'
colnames(maineffects_tlag)[2] <- 'level'

maineffects <- rbind(maineffects_truesynchrony,maineffects_bd,maineffects_tlag,maineffects_timelength,maineffects_noiselevel,maineffects_noisetype)
a <- dcast(maineffects, level ~  synchr_method)
factor <- c('true_synchrony','true_synchrony','true_synchrony','bd','bd','tlag','tlag','timelength','timelength','noiselevel','noiselevel','noisetype','noisetype')
a <- cbind(factor,a)
a
```

# Mixed ANOVA
Significant effects with generalized effect size greater than 0.5 are discussed.

```{r}
Sevenway <- anova_test(
  data = datahenon, dv = MSE_c, wid = id,
  between = c(true_synchrony,bd,tlag,timelength,noiselevel,noisetype), within = synchr_method)
effects_table <- cbind(get_anova_table(Sevenway)$Effect,get_anova_table(Sevenway)$DFn,get_anova_table(Sevenway)[,4],get_anova_table(Sevenway)$p,get_anova_table(Sevenway)$ges)
pvalue <- round(as.numeric(effects_table[,4]),2)
ges <- round(as.numeric(effects_table[,5]),2)
DF <- round(as.numeric(effects_table[,2]),2)
Fvalue <- round(as.numeric(effects_table[,3]),2) 
effects_table <- data.frame(effects_table[,1],DF,Fvalue,pvalue,ges)
colnames(effects_table)[1] <- 'effects'
effects <- effects_table%>%
  arrange(desc(ges))
effects[1:18,]
```

### Interaction between 'timelength' and 'synchr_method'
Mean values of MSEs (defined by correlation) of mutual information change significantly for different time length.

Including mutual information:

```{r}
datahenon2 <- datahenon[datahenon$synchr_method!='MI',]
data1 <- datahenon %>% 
  group_by(synchr_method,timelength) %>% 
  summarise(y_mean = mean(MSE_c))
data1 %>% 
  ggplot() +
  aes(x = timelength, y = y_mean, color = synchr_method) +
  geom_line(aes(group = synchr_method))+ylab('Mean of MSEs')+scale_color_manual(values=c('black','tomato2','tomato4','red','blue','hotpink1','orange','purple','pink','green','tomato4'),name='Synchrony method',labels=c('coherence','JR10','JR2','JR6','JS','KL','phase synchrony','R01','R05','R09','MI'),breaks=c('coherence','JensenRenyi10','JensenRenyi2','JensenRenyi6','JensenShannon','mutual_information','Kullback','phasesynchrony','Renyi01','Renyi05','Renyi09'))+xlab('Time length')
```
### Interaction between 'bd' 'synchr_method' and 'true_synchrony'

Excluding mutual information:

'bd' is '33':

```{r}
datahenon3 <- datahenon2[datahenon2$bd=='33',]
data3 <- datahenon3 %>% 
  group_by(synchr_method,true_synchrony) %>% 
  summarise(y_mean = mean(MSE_c))
data3 %>% 
  ggplot() +
  aes(x = true_synchrony, y = y_mean, group = synchr_method) +
   geom_line(aes(color = synchr_method,linetype=synchr_method))+
  ylab('Mean of MSEs')+scale_color_manual(values=c('black','green','hotpink','red','red','red','blue','purple','purple','purple','orange'),name='Synchrony method')+scale_linetype_manual(values = c("solid", "solid","solid","solid","dashed","dotted","solid","solid","dashed","dotted",'solid'),name='Synchrony method')+xlab('Noise level')+xlab('True synchrony')+scale_x_discrete('True synchrony',labels=c('low','avg','high'),limits=c('rlow','ravg','rhigh'))
```
'bd' is '31':

```{r}
datahenon4 <- datahenon2[datahenon2$bd=='31',]
data4 <- datahenon4 %>% 
  group_by(synchr_method,true_synchrony) %>% 
  summarise(y_mean = mean(MSE_c))
data4 %>% 
  ggplot() +
  aes(x = true_synchrony, y = y_mean, group = synchr_method) +
   geom_line(aes(color = synchr_method,linetype=synchr_method))+
  ylab('Mean of MSEs')+scale_color_manual(values=c('black','green','hotpink','red','red','red','blue','purple','purple','purple','orange'),name='Synchrony method')+scale_linetype_manual(values = c("solid", "solid","solid","solid","dashed","dotted","solid","solid","dashed","dotted",'solid'),name='Synchrony method')+xlab('Noise level')+xlab('True synchrony')+scale_x_discrete('True synchrony',labels=c('low','avg','high'),limits=c('rlow','ravg','rhigh'))+ylim(0,1)

```

### Interaction between 'synchr_method' and 'noiselevel'
The patterns for phase synchrony and coherence change when the noise level changes.

Excluding mutual information:

```{r}
datahenon2 <- datahenon[datahenon$synchr_method!='MI',]
data1 <- datahenon2 %>% 
  group_by(synchr_method,noiselevel) %>% 
  summarise(y_mean = mean(MSE_c))
data1 %>%  ggplot() +
  aes(x = noiselevel, y = y_mean, group = synchr_method) +
   geom_line(aes(color = synchr_method,linetype=synchr_method))+
  ylab('Mean of MSEs')+scale_color_manual(values=c('black','green','hotpink','red','red','red','blue','purple','purple','purple','orange'),name='Synchrony method')+scale_linetype_manual(values = c("solid", "solid","solid","solid","dashed","dotted","solid","solid","dashed","dotted",'solid'),name='Synchrony method')+xlab('Noise level')+ylim(0,0.5)
  

```

### Interaction between 'true_synchrony', 'timelength' and 'synchr_method'
The patterns for mutual information are different when the time length differs.

Excluding mutual information:

'timelength' is '1006':

```{r}
datahenon3 <- datahenon2[datahenon2$timelength=='1006',]
data3 <- datahenon3 %>% 
  group_by(synchr_method,true_synchrony) %>% 
  summarise(y_mean = mean(MSE_c))
data3 %>% 
  ggplot() +
  aes(x = true_synchrony, y = y_mean, group = synchr_method) +
   geom_line(aes(color = synchr_method,linetype=synchr_method))+
  ylab('Mean of MSEs')+scale_color_manual(values=c('black','green','hotpink','red','red','red','blue','purple','purple','purple','orange'),name='Synchrony method')+scale_linetype_manual(values = c("solid", "solid","solid","solid","dashed","dotted","solid","solid","dashed","dotted",'solid'),name='Synchrony method')+xlab('Time length')+scale_x_discrete('True synchrony',labels=c('low','avg','high'),limits=c('rlow','ravg','rhigh'))+ylim(0,1)
```

'timelength' is '10054':

```{r}
datahenon4 <- datahenon2[datahenon2$timelength=='10054',]
data4 <- datahenon4 %>% 
  group_by(synchr_method,true_synchrony) %>% 
  summarise(y_mean = mean(MSE_c))
data4 %>% 
  ggplot() +
  aes(x = true_synchrony, y = y_mean, group = synchr_method) +
   geom_line(aes(color = synchr_method,linetype=synchr_method))+
  ylab('Mean of MSEs')+scale_color_manual(values=c('black','green','hotpink','red','red','red','blue','purple','purple','purple','orange'),name='Synchrony method')+scale_linetype_manual(values = c("solid", "solid","solid","solid","dashed","dotted","solid","solid","dashed","dotted",'solid'),name='Synchrony method')+xlab('Time length')+scale_x_discrete('True synchrony',labels=c('low','avg','high'),limits=c('rlow','ravg','rhigh'))+ylim(0,1)
```


Appendix:
```{r}
colnames(datahenon)[1:7] <- c('synchrony_method','true_synchrony','bd','time_lag','time_length','noise_level', 'noise_type')
Sevenway <- anova_test(
  data = datahenon, dv = MSE_c, wid = id,
  between = c(true_synchrony,bd,time_lag,time_length,noise_level,noise_type), within = synchrony_method)
effects_table <- cbind(get_anova_table(Sevenway)$Effect,Sevenway$ANOVA$DFn
,get_anova_table(Sevenway)[,4],get_anova_table(Sevenway)$p,get_anova_table(Sevenway)$ges)
pvalue <- as.numeric(effects_table[,4])
ges <- as.numeric(effects_table[,5])
DF <- as.numeric(effects_table[,2])
Fvalue <- as.numeric(effects_table[,3]) 
effects_table <- data.frame(effects_table[,1],DF,Fvalue,pvalue,ges)
colnames(effects_table)[1] <- 'effects'
effects <- effects_table%>%
  arrange(desc(ges))
print(xtable(effects, type = "latex"), file = "MSEhc.tex",include.rownames = F)

```
