---
title: "Results (correlations) for henon maps with true synchrony  defined by correlation"
author: "Yuying Tan"
date: "3/31/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

```{r,include=FALSE}
library(maditr)
load('datahenon.RData')
library(Johnson)
library(rstatix)
library(ggpubr)
library(tidyverse)
```

The true synchrony is defined as the values of the results of correlation coefficient.

# General results
Coherence and phase synchrony perform well.

```{r}
datahenon %>%
  group_by(synchr_method) %>%
  summarise(mean_correlation=mean(correlation_c)) %>%
  arrange(desc(mean_correlation))
```

# Overall influnece of data characteristics


```{r}
maineffects_truesynchrony <- datahenon %>%
  group_by(synchr_method,true_synchrony)  %>%
  summarise(mean_correlation=mean(correlation_c))

maineffects_bd <- datahenon %>%
  group_by(synchr_method,bd)  %>%
  summarise(mean_correlation=mean(correlation_c))

maineffects_tlag <- datahenon %>%
  group_by(synchr_method,tlag)  %>%
  summarise(mean_correlation=mean(correlation_c))

maineffects_timelength <- datahenon %>%
  group_by(synchr_method,timelength)  %>%
  summarise(mean_correlation=mean(correlation_c))

maineffects_noiselevel <- datahenon %>%
  group_by(synchr_method,noiselevel)  %>%
  summarise(mean_correlation=mean(correlation_c))

maineffects_noisetype <- datahenon %>%
  group_by(synchr_method,noisetype)  %>%
  summarise(mean_correlation=mean(correlation_c))
colnames(maineffects_bd)[2] <- 'level'
colnames(maineffects_truesynchrony)[2] <- 'level'
colnames(maineffects_timelength)[2] <- 'level'
colnames(maineffects_noiselevel)[2] <- 'level'
colnames(maineffects_noisetype)[2] <- 'level'
colnames(maineffects_tlag)[2] <- 'level'

maineffects <- rbind(maineffects_truesynchrony,maineffects_bd,maineffects_tlag,maineffects_timelength,maineffects_noiselevel,maineffects_noisetype)
a <- rbind(dcast(maineffects_truesynchrony, level ~  synchr_method),
dcast(maineffects_bd, level ~  synchr_method),
dcast(maineffects_tlag, level ~  synchr_method),
dcast(maineffects_timelength, level ~  synchr_method),
dcast(maineffects_noiselevel, level ~  synchr_method),
dcast(maineffects_noisetype, level ~  synchr_method))
factor <- c('true_synchrony','true_synchrony','true_synchrony','bd','bd','tlag','tlag','timelength','timelength','noiselevel','noiselevel','noisetype','noisetype')
a <- cbind(factor,a)
a
```

Distribution for correlations:

# Mixed ANOVA
```{r}
hist(datahenon$correlation_c,main='Correlation')
```


Johnson transformation is implemented to make 'correlation' more normally distributed.

```{r}
c1 <- datahenon$correlation_c
c2 <- -c1+max(c1)+1 # to transform correlation to non-negative
c <- RE.Johnson(c2)
c3 <- c()
for (i in 1:length(c[[4]])) {
  c3[i] <- c[[4]][i]
}
datahenon$cor_trans_c <- c3 

```
The distribution for transformed correlations:

```{r,echo=F}
hist(datahenon$cor_trans_c, main='Transformed correlation')
```
Normality for correlation and transformed correlation:

```{r,echo=F}
ggqqplot(datahenon, "correlation_c", ggtheme = theme_bw()) +
  facet_grid(bd ~ synchr_method, labeller = "label_both")
ggqqplot(datahenon, "cor_trans_c", ggtheme = theme_bw()) +
  facet_grid(bd ~ synchr_method, labeller = "label_both")
```
Levene's test is for checking the homogeneity of variances. All p-values are smaller than 0.05 for the original correlation, which indicates violation of the assumption.

```{r}
datahenon %>%
  group_by(synchr_method) %>%
  levene_test(correlation_c~bd*true_synchrony*noisetype*tlag*timelength*noiselevel)
```
After transformation, the test is significant only for phase coherence and phase synchrony.
 
```{r}
datahenon %>%
  group_by(synchr_method) %>%
  levene_test(cor_trans_c~bd*true_synchrony*noisetype*tlag*timelength*noiselevel)
```

Significant effects with generalized effect size greater than 0.1 are discussed.


```{r}
Sevenway <- anova_test(
  data = datahenon, dv = cor_trans_c, wid = id,
  between = c(true_synchrony,bd,tlag,timelength,noiselevel,noisetype), within = synchr_method)
effects_table <- cbind(get_anova_table(Sevenway)$Effect,get_anova_table(Sevenway)$DFn,get_anova_table(Sevenway)[,4],get_anova_table(Sevenway)$p,get_anova_table(Sevenway)$ges)
pvalue <- as.numeric(effects_table[,4])
ges <- as.numeric(effects_table[,5])
DF <- as.numeric(effects_table[,2])
Fvalue <- as.numeric(effects_table[,3]) 
effects_table <- data.frame(effects_table[,1],DF,Fvalue,pvalue,ges)
colnames(effects_table)[1] <- 'effects'
effects <- effects_table%>%
  arrange(desc(ges))
effects[1:18,]
```

# Interpretation
```{r}
datahenon[,2]<-factor(datahenon[,2],levels=c('rlow','ravg',"rhigh"))
datahenon$timelength <- factor(datahenon$timelength,levels=c('1006','10054'))
datahenon$synchr_method <- factor(datahenon$synchr_method,levels=c('coherence','phasesynchrony','Kullback','Renyi01','Renyi05','Renyi09','JensenShannon','JensenRenyi2','JensenRenyi6','JensenRenyi10','mutual_information'))
datahenon$synchr_method <- factor(datahenon$synchr_method,levels=c('coherence','phasesynchrony','Kullback','Renyi01','Renyi05','Renyi09','JensenShannon','JensenRenyi2','JensenRenyi6','JensenRenyi10','mutual_information'),labels=c('coherence','phase synchrony','KL','R(01)','R(05)','R(09)','JS','JR(2)','JR(6)','JR(10)','MI'))
```
```{r}
data1 <- datahenon %>% 
  group_by(true_synchrony,bd) %>% 
  summarise(y_mean = mean(correlation_c))
data1 %>% 
  ggplot() +
  aes(x = bd, y = y_mean, color = true_synchrony) +
  geom_line(aes(group = true_synchrony))+ylab('Mean of correlations')+ylim(-0.2,1)+xlab('b and d')+scale_x_discrete('b and d',labels=c('0.3 and 0.1','0.3 and 0.3'))+scale_color_manual(values=c('black','tomato2','tomato4','red','blue','hotpink1','orange','purple','pink','green','tomato4'),name='True synchrony',labels=c('low','avg','high'),breaks=c('rlow','ravg','rhigh'))
#data1 %>%
  #ggplot() +
#  aes(x = true_synchrony, y = y_mean, color = bd) +
 # geom_line(aes(group = bd))

```

```{r}
data1 <- datahenon %>% 
  group_by(synchr_method,true_synchrony) %>% 
  summarise(y_mean = mean(correlation_c))
data1 %>% 
  ggplot()+
  aes(x = true_synchrony, y = y_mean, group = synchr_method) +
   geom_line(aes(color = synchr_method,linetype=synchr_method))+
  ylab('Mean of correlations')+scale_color_manual(values=c('black','green','hotpink','red','red','red','blue','purple','purple','purple','orange'),name='Synchrony method')+scale_linetype_manual(values = c("solid", "solid","solid","solid","dashed","dotted","solid","solid","dashed","dotted",'solid'),name='Synchrony method')+xlab('Noise level')+xlab('True synchrony')+scale_x_discrete('True synchrony',labels=c('low','avg','high'),limits=c('rlow','ravg','rhigh'))


```

```{r}
data1 <- datahenon %>% 
  group_by(synchr_method,tlag) %>% 
  summarise(y_mean = mean(correlation_c))
data1 %>% 
  ggplot() +
  aes(x = tlag, y = y_mean, group = synchr_method) +
   geom_line(aes(color = synchr_method,linetype=synchr_method))+
  ylab('Mean of correlations')+scale_color_manual(values=c('black','green','hotpink','red','red','red','blue','purple','purple','purple','orange'),name='Synchrony method')+scale_linetype_manual(values = c("solid", "solid","solid","solid","dashed","dotted","solid","solid","dashed","dotted",'solid'),name='Synchrony method')+xlab('Time lag')
#data1 %>%
  #ggplot() +
#  aes(x = true_synchrony, y = y_mean, color = bd) +
 # geom_line(aes(group = bd))

```

Appendix:
```{r}
options(digits = 2)
colnames(datahenon)[1:7] <- c('synchrony_method','true_synchrony','bd','time_lag','time_length','noise_level', 'noise_type')
Sevenway <- anova_test(
  data = datahenon, dv = cor_trans_c, wid = id,
  between = c(true_synchrony,bd,time_lag,time_length,noise_level,noise_type), within = 
  synchrony_method)
effects_table <- cbind(get_anova_table(Sevenway)$Effect,Sevenway$ANOVA$DFn,get_anova_table(Sevenway)[,4],get_anova_table(Sevenway)$p,get_anova_table(Sevenway)$ges)
pvalue <- as.numeric(effects_table[,4])
ges <- as.numeric(effects_table[,5])
DF <- as.numeric(effects_table[,2])
Fvalue <- as.numeric(effects_table[,3]) 
effects_table <- data.frame(effects_table[,1],DF,Fvalue,pvalue,ges)
colnames(effects_table)[1] <- 'effects'
effects <- effects_table%>%
  arrange(desc(ges))
effects[1:18,]
print(xtable(effects, type = "latex"), file = "Corhc",include.rownames = F)

```
